### 2017-05-31 KineticModel/estimation/docs/formulation/noisy_estimate.tex
include comments from Krishna on model formulation

	The optimization formulation to estimate fluxes given below is based on the minimization of the tolerance for the L2-norm of the difference between the model predicted flux and the noisy flux. 
	\begin{center}
		\begin{subequations}\label{eq:noisyopt}
			\begin{align}
			\underset{x,p}{\mathrm{min}} & \text{      }\varepsilon\\
			\mathrm{st} & \text{      }|v-v^*| \le \varepsilon\\
			& \text{      }|x-x^*| \le \varepsilon\\
			& \text{      }Sv = 0\\
			& \text{      }v = f(x,p)\\
			& \text{      }x_{min}\le x \le x_{max}\\
			& \text{      }p_{min} \le p \le p_{max}
			\end{align}
		\end{subequations}		
	\end{center}

	In Equation (\ref{eq:noisyopt}) above, $\varepsilon$ is the absolute tolerance between the predicted and the measured quantities. The relationship between the predicted and the measured quantities are given by the nonlinear constraints in Equations (\ref{eq:noisyopt}b) and (\ref{eq:noisyopt}c). The stoichiometric constraints for steady state are given by Equation (\ref{eq:noisyopt}d), and Equation (\ref{eq:noisyopt}e) specifies the kinetic rate laws for the predicted fluxes as a function of the concentrations ($x$) and the parameters ($p$). Equations (\ref{eq:noisyopt}f) and (\ref{eq:noisyopt}g) are the bounds for the concentrations and parameters that are to be estimated by the optimization problem.

>>>>

	The optimization formulation to estimate fluxes given below is based on the minimization of the tolerance for the L2-norm of the difference between the model predicted flux and the noisy flux. 
	\begin{center}
		\begin{subequations}\label{eq:noisyopt}
			\begin{align}
			\underset{x,p}{\mathrm{min}} & \text{      }e\\
			\mathrm{st} & \text{      }|v-v^*| \le \varepsilon\\
			& \text{      }|x-x^*| \le \varepsilon\\
			& \text{      }Sv = 0\\
			& \text{      }v = f(x,p) + e\\
			& \text{      }x_{min}\le x \le x_{max}\\
			& \text{      }p_{min} \le p \le p_{max}			
			\end{align}
		\end{subequations}		
	\end{center}

	In Equation (\ref{eq:noisyopt}) above, $\varepsilon$ is the absolute tolerance between the predicted and the measured quantities. The relationship between the predicted and the measured quantities are given by the nonlinear constraints in Equations (\ref{eq:noisyopt}b) and (\ref{eq:noisyopt}c). The stoichiometric constraints for steady state are given by Equation (\ref{eq:noisyopt}d), and Equation (\ref{eq:noisyopt}e) specifies the kinetic rate laws for the predicted fluxes as a function of the concentrations ($x$) and the parameters ($p$). Equations (\ref{eq:noisyopt}f) and (\ref{eq:noisyopt}g) are the bounds for the concentrations and parameters that are to be estimated by the optimization problem. The above optimization problem is to be solved for fixed values of $\varepsilon \in \{\text{.01, .05, .1}\}$.
